WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-03-02 method/sec_4-db_struct.tex
Tried href links package
Draft paper up to lit review
Used PDF and removed JMeter images
Replace noun acronym with full word

To understand the underline design decisions of the \acrshort{wdias} database structure, it needs to deeply look into the weather data timeseries.
\paragraph{Timeseries}-- \emph{A timeseries is simply a series of data points ordered in time}. In the weather domain, its interest in timeseries in perspective of observations to forecasting. Each timeseries, the data points can be formed in different formats as well. For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/microservice/wdias_database_structure.jpg}
    \caption{\acrshort{wdias} database structure}
    \label{fi:database_structure}
\end{figure}

@@

\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
Since the \acrshort{wdias} scope is to use open source tools, it is using \acrshort{mysql} as a persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be described in more detail \cref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
As mentioned in \cref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
\gkc{ADDED}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{is using a unique database indexing algorithm to gain higher performance while storing timeseries data} when compared to other databases available. Also, it has better support, higher usage and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer that will give the required performance. Going further, users can use the commercial version of \acrshort{influxdb} to gain more performance.

Two instances of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \emph{Database per Service} as mentioned in \cref{subse:database_per_service}.
But further, it split into two services, referring to \cref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among a few servers based on valueType key attribute of timeseries.
Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.

@@

\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented database, as it has the Geo searching capabilities.
\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database. And it supports:
\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of WDIAS above.}
\gkc{Adding those details in \cref{se:high_level_design} may confuse the reader. At that point it didn't go through that much of details of the wdias. I added some justification at the end of \cref{subse:timeseries_key_attributes}. Let me know if we want to highlight it with a different section there.}
\begin{itemize}
  \item Supports query operations on geospatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
\acrshort{mongodb} geospatial features are using to support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}. Vise a versa, if new timeseries create in the adapter-metadata, it triggers an event to adapter-query to index the new timeseries.
In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale of the system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as a key-value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates on \cref{se:data_preprocess}

>>>>

The foundation of the \acrshort{wdias} is data-centric. To understand the underline design decisions of the \acrshort{wdias} database structure, it needs to deeply look into the weather data timeseries.
\paragraph{Timeseries}-- \emph{A timeseries is simply a series of data points ordered in time}. In the weather domain, its interest in timeseries in perspective of observations to forecasting. Each timeseries, the data points can be formed in different formats as well. For example, scalar (0D), vector (1D), grid (2D), and polygon (2D).

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{method/microservice/wdias_database_structure.pdf}
    \caption{\acrshort{wdias} database structure}
    \label{fi:database_structure}
\end{figure}

@@

\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
Since the \acrshort{wdias} scope is to use open source tools, it is using  MySQL as a persistent database for storing timeseries metadata described above.
One instance of  MySQL is using only by adapter-metadata service.
Other than that, another instance of  MySQL is using for adapter-extension which will be described in more detail \cref{se:data_preprocess}.
 MySQL is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
As mentioned in \cref{subse:redis}, it uses  Redis instance is using for caching the data from  MySQL, since the  MySQL database instances, itself not going to get much load.
Other than MySQL, many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
\gkc{ADDED}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases,  InfluxDB \cite{influxdbInfluxDBDocumentation} \hl{is using a unique database indexing algorithm to gain higher performance while storing timeseries data} when compared to other databases available. Also, it has better support, higher usage and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than  InfluxDB, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the  InfluxDB, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
 InfluxDB can setup on a computer that will give the required performance. Going further, users can use the commercial version of  InfluxDB to gain more performance.

Two instances of  InfluxDB is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \emph{Database per Service} as mentioned in \cref{subse:database_per_service}.
But further, it split into two services, referring to \cref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among a few servers based on valueType key attribute of timeseries.
Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.

@@

\acrshort{wdias} is using  MongoDB as the document-oriented database, as it has the Geo searching capabilities.
 MongoDB \cite{mongodbMongoDBManual} is a general-purpose, document-based, distributed database. And it supports:
\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of WDIAS above.}
\gkc{Adding those details in \cref{se:high_level_design} may confuse the reader. At that point it didn't go through that much of details of the wdias. I added some justification at the end of \cref{subse:timeseries_key_attributes}. Let me know if we want to highlight it with a different section there.}
\begin{itemize}
  \item Supports query operations on geospatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
 MongoDB geospatial features are using to support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query if fetch data from the adapter-metadata, then indexed and cache in the  MongoDB. Vise a versa, if new timeseries create in the adapter-metadata, it triggers an event to adapter-query to index the new timeseries.
In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale of the system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using  Redis \cite{redisRedisDocumentation} as the In-Memory database, since it is a widely used tool with good support, and it supports few other features such as Publisher Subscriber capabilities.
 Redis is an open-source (BSD licensed), used as a database, cache. Clustering is available for scalability.
 Redis uses as in-memory caching for fast access the frequent access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses  Redis as a key-value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities to create a cronjob in extension-scheduler when a new extension creates on \cref{se:data_preprocess}

### 2020-03-02 method/sec_5-data_preprocess.tex
Replace noun acronym with full word

To improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms. For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint. First, other than storing extension metadata in MySQL instance of adapter-extension, it also stores the data in reverse lookup table called triggers. Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries. Thus, the response which is received by the 
extension-handler only contains the extensions to be triggered. No additional filtering needs to be done at the extension-handler service.
Second, cache the resulting trigger\_type and timeseries data in the \acrshort{redis} database for fast access and avoid too many queries on the \acrshort{mysql} database.

\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value. To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
Same as for extension-handler, the adapter-extension exposes an endpoint to retrieve extension metadata grouped by cronjob time. Then use \acrshort{go} to implement the extension-handler to fast processing the extensions. After retrieve extensions which is grouped by cronjob time; within the extension-handler, it schedules programmatic cronjobs to trigger at given times. When each cronjob triggers at the given time, it also contains the extensions to be triggered. Fetching extension data and creating cronjobs occur with a long period to avoid heavy overhead.
When a new extension trigger created, those data push into a \acrshort{redis} list. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
As mentioned above, to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cronjobs.
The extension-handler should be run as a single entity for the atrocity, to avoid triggering the same extension twice.

>>>>

To improve the performance of matching triggers against a timeseries, the WDIAS added two mechanisms. For the separation of service responsibilities, those functionalities reside in the adapter-extension and expose via an endpoint. First, other than storing extension metadata in MySQL instance of adapter-extension, it also stores the data in reverse lookup table called triggers. Using this reverse lookup table, for a given trigger\_type and timeseries, it can retrieve the extensions which are part of given timeseries. Thus, the response which is received by the 
extension-handler only contains the extensions to be triggered. No additional filtering needs to be done at the extension-handler service.
Second, cache the resulting trigger\_type and timeseries data in the  Redis database for fast access and avoid too many queries on the  MySQL database.

\paragraph{Extension Scheduler}-- Extension Handler is responsible for triggering the correct Extension with metadata at a given time which is provided at the creation on extension trigger with the value of OnTime cronjob string value. To improve the performance of triggering cronjobs at given time schedules, the WDIAS added few optimization mechanisms.
Same as for extension-handler, the adapter-extension exposes an endpoint to retrieve extension metadata grouped by cronjob time. Then use \acrshort{go} to implement the extension-handler to fast processing the extensions. After retrieve extensions which is grouped by cronjob time; within the extension-handler, it schedules programmatic cronjobs to trigger at given times. When each cronjob triggers at the given time, it also contains the extensions to be triggered. Fetching extension data and creating cronjobs occur with a long period to avoid heavy overhead.
When a new extension trigger created, those data push into a  Redis list. Then pulling from the extension-handler in regular time intervals and create new cronjobs for mentioned cronjob time.
As mentioned above, to avoid the expansion of the programmatic cronjob list which are created for new extension triggers, all cronjobs fetch again in a long period and flush the previously scheduled cronjobs.
The extension-handler should be run as a single entity for the atrocity, to avoid triggering the same extension twice.

### 2020-03-02 results/sec_2-workload.tex
WDIAS_Thesis_v3.2
Replace noun acronym with full word

In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomized} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector, and 10\% Grid as mentioned in \cref{se:test_plan}.
Before running the test cases, it generates the metadata for timeseries and writes into a CSV file which is shared among the threads in the \acrshort{jmeter}. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within every 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

The system is capable of storing any numeric value up to 3 decimal points. It does not make any difference based on the parameter type whether it is the precipitation or the temperature. Thus during the performance testing, \acrshort{jmeter} uses real precipitation data from \acrshort{curw}. One month period of data for five weather stations has been using to prepare the test data. The script to clean up and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.

\begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_precipitation.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_precipitation.sh prepare
    Segregate single file data into multiple files based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_precipitation.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_precipitation.sh cleanup
    Clean up extracted directories
\end{lstlisting}
When preparing the data, it creates three sets of data based on the time interval such as hourly (60min), 30min, and 15min data with modifying the replicated data.
This will reduce the overhead in performance testing and increase the performance itself.
Extract function use while creating the containers, and extract the data into the container. This reduces the context loading while creating the container images.
While performing the load testing, \acrshort{jmeter} keeps update a date counter and creates over the one-month data. At the end of the current month, the date counter advance to the next month. But data is repeated using from the beginning. To provide more randomness, it switches over five locations as well. The JSR223 scripts were written generically such that is possible to tweak and use if there are more location data available.

@@

\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted directories
\end{lstlisting}
The water level also contains the real data for one month of period and \emph{setup\_waterlevel.sh} script provides the functionality of preparation, cleanup, and extract.
Also, it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keeps increasing.

@@

To create a higher workload using the \acrshort{jmeter}, it has a Distributed Testing feature. It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances. But it has the following limitation of \emph{the same test plan runs by all the servers}. \acrshort{jmeter} does not distribute the load between servers, each runs the full test plan. So if you set 1,000 threads and have 6 \acrshort{jmeter} servers, you end up injecting 6,000 threads. When test cases run with \acrshort{jmeter} Distributed mode, the server node trigger the same copy of the test case on configured slave nodes parallel. At the end of the test cases, it gathers results into the master node.

@@

When implementing load test cases with \acrshort{jmeter}, it uses threads to simulate the users. The root component of a test create is a thread group. There are different kinds of thread groups are available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Closed vs. open workload models}
\label{subse:closed_vs_open_workload}
\begin{itemize}
    \item \emph{closed system model} \cite{Haggett1998AnWales} -- a new request is only triggered by the completion of a previous request, following by a think time. The system has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
    \item \emph{open system model} -- new requests arrival independently of completions, e.g., according to a stochastic process or fixed trace. The system has no negative feedback.
\end{itemize}
While implementing the test cases for \acrshort{wdias}, it uses the Concurrency Thread Group with Throughput Shaping Timer because it supports the open workload approach.
Using other thread groups, it required to find the exact number of threads and timer delays that produce the desired number of \acrfull{rps} to server. It is known as the \emph{closed workload}.
With using \emph{Throughput Shaping Timer}, it only needs to configure the \acrshort{rps}. When combining this \acrshort{jmeter} plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The test plans mentioned in \cref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:

@@

By creating the timeseries before help to reduce the overhead during the performance testing, and cause to more accurate \acrshort{rps} at the run time.
Otherwise, \acrshort{jmeter} needs to allocate another set of threads for timeseries creation. Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather than creating new timeseries in the \acrshort{wdias} system.

The following list shows the test steps of \acrshort{jmeter} while performing the load testing and the configurations.

@@

With the above \acrshort{jmeter} test case setup, it needs to enable each test case separately and before running via the command line in the server. To do it in a much efficient way, a scripting tool has implemented, and accessible with the codebase \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Test System Setup}}
\label{subse:test_sys_config}
As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focused on microservice architecture and implemented on top of Kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.

@@

Users can use one of the above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts use node Affinity to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} -- \acrshort{jmeter} and metric server
\end{itemize}
\cref{fi:eks_node_setup} shows the overview of the show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
The databases used for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDB are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for the grid data type. To keep up with the pace, those microservice pods are assigned to dedicated nodes to increase the performance of inter-service communication.

>>>>

In the  JMeter Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomized} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector, and 10\% Grid as mentioned in \cref{se:test_plan}.
Before running the test cases, it generates the metadata for timeseries and writes into a CSV file which is shared among the threads in the  JMeter. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within every 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

The system is capable of storing any numeric value up to 3 decimal points. It does not make any difference based on the parameter type whether it is the precipitation or the temperature. Thus during the performance testing,  JMeter uses real precipitation data from \acrshort{curw}. One month period of data for five weather stations has been using to prepare the test data. The script to clean up and prepare the precipitation data is available as \emph{setup\_precipitation.sh} in wdias-performance.

\begin{lstlisting}[language=sh, caption=Preparation of precipitation data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_precipitation.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_precipitation.sh prepare
    Segregate single file data into multiple files based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_precipitation.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_precipitation.sh cleanup
    Clean up extracted directories
\end{lstlisting}
When preparing the data, it creates three sets of data based on the time interval such as hourly (60min), 30min, and 15min data with modifying the replicated data.
This will reduce the overhead in performance testing and increase the performance itself.
Extract function use while creating the containers, and extract the data into the container. This reduces the context loading while creating the container images.
While performing the load testing,  JMeter keeps update a date counter and creates over the one-month data. At the end of the current month, the date counter advance to the next month. But data is repeated using from the beginning. To provide more randomness, it switches over five locations as well. The JSR223 scripts were written generically such that is possible to tweak and use if there are more location data available.

@@

\begin{lstlisting}[language=sh, caption= Preparation of water-level data.]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted directories
\end{lstlisting}
The water level also contains the real data for one month of period and \emph{setup\_waterlevel.sh} script provides the functionality of preparation, cleanup, and extract.
Also, it reset and repeat reading from the beginning when the  JMeter date counter keeps increasing.

@@

To create a higher workload using the  JMeter, it has a Distributed Testing feature. It uses the master-slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances. But it has the following limitation of \emph{the same test plan runs by all the servers}.  JMeter does not distribute the load between servers, each runs the full test plan. So if you set 1,000 threads and have 6  JMeter servers, you end up injecting 6,000 threads. When test cases run with  JMeter Distributed mode, the server node trigger the same copy of the test case on configured slave nodes parallel. At the end of the test cases, it gathers results into the master node.

@@

When implementing load test cases with  JMeter, it uses threads to simulate the users. The root component of a test create is a thread group. There are different kinds of thread groups are available such as thread group (basic thread group), arrivals thread Group, free form arrivals thread group, stepping thread group, concurrency thread group, and ultimate thread group.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Closed vs. open workload models}
\label{subse:closed_vs_open_workload}
\begin{itemize}
    \item \emph{closed system model} \cite{Haggett1998AnWales} -- a new request is only triggered by the completion of a previous request, following by a think time. The system has negative feedback that makes it impossible to bury-out the service, so users wait for the responses before making new requests.
    \item \emph{open system model} -- new requests arrival independently of completions, e.g., according to a stochastic process or fixed trace. The system has no negative feedback.
\end{itemize}
While implementing the test cases for \acrshort{wdias}, it uses the Concurrency Thread Group with Throughput Shaping Timer because it supports the open workload approach.
Using other thread groups, it required to find the exact number of threads and timer delays that produce the desired number of \acrfull{rps} to server. It is known as the \emph{closed workload}.
With using \emph{Throughput Shaping Timer}, it only needs to configure the \acrshort{rps}. When combining this  JMeter plugin with Concurrency Thread Group using Schedule Feedback Function to dynamically maintain thread count required to achieve target \acrshort{rps} \cite{KarunarathneGihanWdias/wdias-performance-test:JMeter.}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The test plans mentioned in \cref{se:test_plan} are implemented via the  JMeter. The following list shows the all the test cases used for the performance testing:

@@

By creating the timeseries before help to reduce the overhead during the performance testing, and cause to more accurate \acrshort{rps} at the run time.
Otherwise,  JMeter needs to allocate another set of threads for timeseries creation. Since the test cases insert data again set of timeseries, most of the time it about retrieving the timeseries metadata, rather than creating new timeseries in the \acrshort{wdias} system.

The following list shows the test steps of  JMeter while performing the load testing and the configurations.

@@

With the above  JMeter test case setup, it needs to enable each test case separately and before running via the command line in the server. To do it in a much efficient way, a scripting tool has implemented, and accessible with the codebase \cite{KarunarathneWdias-performance-test/TEST_PLAN.md:Plan} as \emph{test-dev}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Test System Setup}}
\label{subse:test_sys_config}
As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focused on microservice architecture and implemented on top of Kubernetes. \acrfull{k8s} is an open-source system which is capable of automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.

@@

Users can use one of the above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts use node Affinity to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} --  JMeter and metric server
\end{itemize}
\cref{fi:eks_node_setup} shows the overview of the show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
The databases used for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDB are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for the grid data type. To keep up with the pace, those microservice pods are assigned to dedicated nodes to increase the performance of inter-service communication.

### 2020-03-02 results/sec_3-observations.tex
Paper: performance analysis
Replace noun acronym with full word

\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled overtime. The auto-scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%. And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart. While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization. After \acrshort{k8s} spawn 10 maximum pods, it stops spawning new pods. But the pods were able to perform with vertical scaling since those are not hit the CPU limit of 2.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
    \caption{Load testing with auto-scaling resource usage of database adapters.}
    \label{fi:obs_all_auto_15m_adapter_dbs_res}
\end{figure}
\cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.

@@

\cref{tab:obs_query_15_min_summary} shows the response latency summary details. The average latency is much higher than the minimum value. Also, it reported higher maximum values as well. Standard deviation showed a quiet higher value which means the response latency values are not closer to the average value. Noticeably, it does not report any errors, which means all the requests successfully process.
The throughput for each test case is much higher and similar to all the requests. This is happening since all of these requests are handled via the adapter-query, it depends on the \acrshort{mongodb} database performance.

@@

Whenever the timeseries data not found in the adapter-query, it read data from adapter-metadata and index for search over timeseries metadata. This will cause to higher performance with geo timeseries searches. The performance of the \acrshort{mongodb} can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
Those attempts are beyond the scope of the \acrshort{wdias} performance test and users can use those to get higher results from the \acrshort{wdias}.

>>>>

\cref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled overtime. The auto-scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%. And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart. While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization. After \acrshort{k8s} spawn 10 maximum pods, it stops spawning new pods. But the pods were able to perform with vertical scaling since those are not hit the CPU limit of 2.
\cref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
    \caption{Load testing with auto-scaling resource usage of database adapters.}
    \label{fi:obs_all_auto_15m_adapter_dbs_res}
\end{figure}

@@

\cref{tab:obs_query_15_min_summary} shows the response latency summary details. The average latency is much higher than the minimum value. Also, it reported higher maximum values as well. Standard deviation showed a quiet higher value which means the response latency values are not closer to the average value. Noticeably, it does not report any errors, which means all the requests successfully process.
The throughput for each test case is much higher and similar to all the requests. This is happening since all of these requests are handled via the adapter-query, it depends on the  MongoDB database performance.

@@

Whenever the timeseries data not found in the adapter-query, it read data from adapter-metadata and index for search over timeseries metadata. This will cause to higher performance with geo timeseries searches. The performance of the  MongoDB can further improve with using its features like Replication for high availability, and Sharding for higher throughput.
Those attempts are beyond the scope of the \acrshort{wdias} performance test and users can use those to get higher results from the \acrshort{wdias}.

### 2020-03-02 results/sec_4-discussion.tex
Replace noun acronym with full word

One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data. Further, it is possible to increase the performance of these bottlenecks much higher such as using the \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.

>>>>

One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as  InfluxDB for Scalar and Vector data, and netCDF with parallel support for Grid data. Further, it is possible to increase the performance of these bottlenecks much higher such as using the  InfluxDB Commercial cluster support for high availability or horizontal scaling of  InfluxDB. With  InfluxDB cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
